Compile Time Verification of Deterministic properties for Sequential Programs

### 2019-03-14 paper.tex
Intro start

Text of paper \ldots

>>>>

Writing correct programs is hard. Programmers often write correctness specifications for their code in the form of assertions. They write test cases that cover several usage scenarios to strengthen their belief that
the code works as intended. Despite all the testing effort, it often happens that a test suite produces
diverging results for different users or for the same user when the test suite is run again. When a test suite fails
nondeterministically, it  reduces the programmers' confidence in the program. Additionally, reproducing
such bugs is difficult making debugging an onerous task. Examples of the underlying causes of such flakiness 
could be OS scheduling in case of concurrent programs, use of an API that has nondeterministic specification,
accessing system properties such as the file system or environment variables. In this paper, we focus on
nondeterminism arising from the usage of APIs that have nondeterministic specifications in java programs.
Instances of such APIs in the JDK include Date(), Random(), iterating over a HashSet. Note that mere calls
to these APIs is not problematic. But if the programmer intends the results of these calls to be deterministic,
it could result in undesirable results and we aim to capture this behavior and report it. The high level goal
of our work is to provide programmers with a tool for specifying  deterministic properties ina program
and be able to verify them at compile time.

Ideally with any program, we expect the output to be the same.
Example sources of nondeterminism

Test suites, production environemnt, Flakiness, recent work in this area

Dependency on APIs , Talk about specifications

Approach is to build a type system

Focus on collections

Ease of extensibility of our approach

We make the folowing contributions through this paper:
\begin{enumerate}
	\item Design and implement a type system for expressing deterministic properties in sequential programs.
	\item Annotate several classes in JDK. By doing this, we have translated the specification for these APIs from
	human readable comments to machine readable and verifyable documentation.
	\item Perform a case study of a real work Java program - Randoop (loc, etc) which revealed bugs.
	\item Compare our technique to flaky test detectors and present results.
\end{enumerate}

\section{Design}
